Analysis

### 2020-01-16 script/analysis.Rmd
real vs percibido obrero gerente
.

ggsave(salario_justo_real,filename = "output/images/salario_justo_real.png",device = "png",width = 20,height = 15,dpi = "retina",units = "cm")
```

>>>>

ggsave(salario_justo_real,filename = "output/images/salario_justo_real.png",device = "png",width = 20,height = 15,dpi = "retina",units = "cm")
```
## real vd percibido

table_perrialob <-rbind(table_perob ,salario_obrero)
str(table_justot)

table_perrialob

table_perrialob$ocup2 <- factor(table_perrialob$ocup, levels=c(1,3), labels=c("Salario percibido Obrero","Salario real Obrero"))

table_perrialob <- ggplot(data=table_perrialob, aes(x=reorder(as.factor(year),-year), y=median, fill=ocup2)) +
     geom_bar(position = 'dodge', stat='identity') +
     geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), y=0), position=position_dodge(0.9), hjust=-0.25) +
     theme_bw(base_size = 12) +
     scale_y_continuous(labels = scales::comma) +
     ylab('Salario (mediana)') + xlab('Años') +
     scale_fill_brewer(palette="Paired") +
     theme(legend.position="top") +
     labs(fill = " ") +
     guides(fill = guide_legend(reverse = TRUE)) +
    coord_flip()
ggsave(table_perrialob,filename = "output/images/table_perrialob.png",device = "png",width = 30,height = 15,dpi = "retina",units = "cm")

table_perrialob

```{r}
table_perriager <-rbind(table_perger ,salario_gerente)
str(table_justot)

table_perrialob

table_perriager$ocup2 <- factor(table_perriager$ocup, levels=c(2,4), labels=c("Salario percibido Gerente","Salario real Gerente"))

table_perriager <- ggplot(data=table_perriager, aes(x=reorder(as.factor(year),-year), y=median, fill=ocup2)) +
     geom_bar(position = 'dodge', stat='identity') +
     geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), y=0), position=position_dodge(0.9), hjust=-0.25) +
     theme_bw(base_size = 12) +
     scale_y_continuous(labels = scales::comma) +
     ylab('Salario (mediana)') + xlab('Años') +
     scale_fill_brewer(palette="Paired") +
     theme(legend.position="top") +
     labs(fill = " ") +
     guides(fill = guide_legend(reverse = TRUE)) +
    coord_flip()
ggsave(table_perrialob,filename = "output/images/table_perriager.png",device = "png",width = 30,height = 15,dpi = "retina",units = "cm")

table_perriager
```
